01\_Thresholding\_local

### 2018-03-15 notebook.tex
wrote manuscript

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{Thresholding\_local}

@@

In this notebook, I extract orbits for a signle chromosome in all 4 cell
lines, using a different method of thresholding. In order to do this, I
slide a kernel of size k through each pixel and check if it has a
particular property. If the property is satisified, then the pixel is
set to 1, otherwise it is set to 0. The two properties that I experiment
with are \emph{maximum thresholding} and \emph{normal thresholding}. 1.
\textbf{Maximum Thresholding}: in max thresholding, if the pixel is the
maximum of its neighbors with respect to the kernel, then it is set. 2.
\textbf{Normal Thresholding}: in normal thresholding, if the pixel is
larger that the average of the neighbors then it is set.

first I perform the most lates normalization method that I have found to
be most useful: a combination of gaussian normalization, SCN and pearson
correlation, in the same order mentioned. The normalized results are of
type \texttt{pearson(scn(gaussian(graph)))}.

Then I threshold the results by setting pearson values larger than 0 to
1 and the rest to 0. In order to extract graphlets, I used the
\emph{orca} package in R. the script \texttt{./rscript.r} read a binary
thresholded matrix representing an unweighted graph and outputs orbtis 0
through 72 for each node in the network. After thredholding the
matrices, I save them so that orca in R can read it and extract orbits.

By repeating the procedure explained above for all 23 chromosomes, we
will have graphlets for all contact maps.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}5}]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
        \PY{k+kn}{import} \PY{n+nn}{cv2}
        \PY{k+kn}{from} \PY{n+nn}{utility} \PY{k+kn}{import} \PY{o}{*}
        \PY{k+kn}{import} \PY{n+nn}{matplotlib.pyplot} \PY{k+kn}{as} \PY{n+nn}{plt}
        \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n}{normalization}
        \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n+nb}{filter}
        \PY{k+kn}{import} \PY{n+nn}{os}
        \PY{o}{\PYZpc{}}\PY{k}{load\PYZus{}ext} autoreload
        \PY{o}{\PYZpc{}}\PY{k}{autoreload} 2
        \PY{o}{\PYZpc{}}\PY{k}{pylab} inline
        \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
The autoreload extension is already loaded. To reload it, use:
  \%reload\_ext autoreload
Populating the interactive namespace from numpy and matplotlib

@@

    \begin{Verbatim}[commandchars=\\\{\}]
/home/bzr0014/watson/scripts/virt/local/lib/python2.7/site-packages/IPython/core/magics/pylab.py:161: UserWarning: pylab import has clobbered these variables: ['all', 'colors', 'log']
`\%matplotlib` prevents importing * from pylab and numpy
  "\textbackslash{}n`\%matplotlib` prevents importing * from pylab and numpy"

@@

    \subsection{Initiating matrices}\label{initiating-matrices}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}18}]:} \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{2}
         \PY{n}{chr2} \PY{o}{=} \PY{n}{chr1}
         \PY{k}{print} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{chromosome 1: }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{, chromosome 2: }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
         \PY{c+c1}{\PYZsh{}print observed\PYZus{}mit\PYZus{}original.shape}

@@

         \PY{c+c1}{\PYZsh{}There are some blank rows and columns in the matrix. let\PYZsq{}s remove them.}
         \PY{n}{blankRows0}\PY{p}{,} \PY{n}{blankCols0} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
         \PY{n}{blankRows1}\PY{p}{,} \PY{n}{blankCols1} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}
         \PY{n}{blankRows2}\PY{p}{,} \PY{n}{blankCols2} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{rl}\PY{p}{)}
         \PY{n}{blankRows3}\PY{p}{,} \PY{n}{blankCols3} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{call4}\PY{p}{)}
         \PY{n}{blankRows} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
         \PY{n}{blankCols} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows0}\PY{p}{)}
         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows1}\PY{p}{)}
         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows2}\PY{p}{)}
         \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows3}\PY{p}{)}
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols0}\PY{p}{)}
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols1}\PY{p}{)}
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols2}\PY{p}{)}
         \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols3}\PY{p}{)}
         \PY{n}{mit} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
         \PY{n+nb}{all} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n+nb}{all}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
         \PY{n}{rl} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{rl}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
         \PY{n}{call4} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{call4}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
chromosome 1: 2, chromosome 2: 2
file directory: ../data/extracted\_all\_contact\_MIT/chr\_02\_02\_500kb.mat
file directory: ../data/extracted\_all\_contact\_call4/chr\_02\_02\_500kb.mat
file directory: ../data/extracted\_all\_contact\_RL/chr\_02\_02\_500kb.mat
file directory: ../data/extracted\_all\_contact\_ALL/chr\_02\_02\_500kb.mat
size of old matrix: (486, 486)
size of new matrix: (480, 480)
size of old matrix: (486, 486)
size of new matrix: (480, 480)
size of old matrix: (486, 486)
size of new matrix: (480, 480)
size of old matrix: (486, 486)
size of new matrix: (480, 480)

@@

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}19}]:} \PY{n}{n0}\PY{p}{,} \PY{n}{m0} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
         \PY{n}{n1}\PY{p}{,} \PY{n}{m1} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{call4}\PY{p}{)}
         \PY{n}{n2}\PY{p}{,} \PY{n}{m2} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{rl}\PY{p}{)}
         \PY{n}{n3}\PY{p}{,} \PY{n}{m3} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}

@@

    \begin{verbatim}
<matplotlib.figure.Figure at 0x7f65c3721610>
    \end{verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_4_2.png}
    \end{center}
    { \hspace*{\fill} \\}

>>>>

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{01\_Thresholding\_local}

@@

In this notebook, I extract orbits for a signle chromosome in all 4 cell
lines, using a different method of thresholding. In order to do this, I
slide a kernel of size k through each pixel and check if it has a
particular property. If the property is satisified, then the pixel is
set to 1, otherwise it is set to 0. The two properties that I experiment
with are \emph{maximum thresholding} and \emph{normal thresholding}. 1.
\textbf{Maximum Thresholding}: in max thresholding, if the pixel is the
maximum of its neighbors with respect to the kernel, then it is set.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{def}\NormalTok{ local_threshold(mat, k}\OperatorTok{=}\DecValTok{1}\NormalTok{, method}\OperatorTok{=}\StringTok{'max'}\NormalTok{, t}\OperatorTok{=}\DecValTok{1}\NormalTok{):}
\NormalTok{    mat2 }\OperatorTok{=}\NormalTok{ np.zeros_like(mat)}
\NormalTok{    n, m }\OperatorTok{=}\NormalTok{ mat.shape}
    \ControlFlowTok{if} \BuiltInTok{isinstance}\NormalTok{(k, }\BuiltInTok{tuple}\NormalTok{):}
\NormalTok{        k1, k2 }\OperatorTok{=}\NormalTok{ k}
    \ControlFlowTok{else}\NormalTok{:}
\NormalTok{        k1 }\OperatorTok{=}\NormalTok{ k2 }\OperatorTok{=}\NormalTok{ k}
    \ControlFlowTok{for}\NormalTok{ i }\KeywordTok{in} \BuiltInTok{range}\NormalTok{(k1, n}\OperatorTok{-}\NormalTok{k1):}
        \ControlFlowTok{for}\NormalTok{ j }\KeywordTok{in} \BuiltInTok{range}\NormalTok{(k, m}\OperatorTok{-}\NormalTok{k2):}
            \ControlFlowTok{if}\NormalTok{ method }\OperatorTok{==} \StringTok{'max'}\NormalTok{:}
\NormalTok{                condition }\OperatorTok{=}\NormalTok{ mat[i, j] }\OperatorTok{==}\NormalTok{ np.}\BuiltInTok{max}\NormalTok{(mat[i}\OperatorTok{-}\NormalTok{k1:i}\OperatorTok{+}\NormalTok{k1, j}\OperatorTok{-}\NormalTok{k2:j}\OperatorTok{+}\NormalTok{k2])}
            \ControlFlowTok{elif}\NormalTok{ method}\OperatorTok{==}\StringTok{'normal'}\NormalTok{:}
\NormalTok{                temp }\OperatorTok{=}\NormalTok{ mat[i}\OperatorTok{-}\NormalTok{k1:i}\OperatorTok{+}\NormalTok{k1, j}\OperatorTok{-}\NormalTok{k2:j}\OperatorTok{+}\NormalTok{k2]}
\NormalTok{                condition }\OperatorTok{=}\NormalTok{ mat[i, j] }\OperatorTok{>=}\NormalTok{ np.mean(temp) }\OperatorTok{+}\NormalTok{ t }\OperatorTok{*}\NormalTok{ np.std(temp)}
            \ControlFlowTok{elif}\NormalTok{ method }\OperatorTok{=} \StringTok{'max_linear'}\NormalTok{:}
\NormalTok{                condition }\OperatorTok{=}\NormalTok{ mat[i, j] }\OperatorTok{==}\NormalTok{ np.}\BuiltInTok{max}\NormalTok{(mat[i, j}\OperatorTok{-}\NormalTok{k1:j}\OperatorTok{+}\NormalTok{k2])}
            \ControlFlowTok{if}\NormalTok{ condition:}
\NormalTok{                mat2[i, j] }\OperatorTok{=} \DecValTok{1}
    \ControlFlowTok{return}\NormalTok{ mat2}
\end{Highlighting}
\end{Shaded}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  \textbf{Normal Thresholding}: in normal thresholding, if the pixel is
  larger that the average of the neighbors then it is set.
\end{enumerate}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}1}]:} \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
        \PY{k+kn}{import} \PY{n+nn}{cv2}
        \PY{k+kn}{from} \PY{n+nn}{utility} \PY{k+kn}{import} \PY{o}{*}
        \PY{k+kn}{import} \PY{n+nn}{matplotlib.pyplot} \PY{k+kn}{as} \PY{n+nn}{plt}
        \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n}{normalization}
        \PY{k+kn}{from} \PY{n+nn}{iced} \PY{k+kn}{import} \PY{n+nb}{filter}
        \PY{k+kn}{import} \PY{n+nn}{os}
        \PY{o}{\PYZpc{}}\PY{k}{load\PYZus{}ext} autoreload
        \PY{o}{\PYZpc{}}\PY{k}{autoreload} 2
        \PY{o}{\PYZpc{}}\PY{k}{pylab} inline
        \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Populating the interactive namespace from numpy and matplotlib

@@

    \begin{Verbatim}[commandchars=\\\{\}]
/home/bzr0014/watson/scripts/virt/local/lib/python2.7/site-packages/IPython/core/magics/pylab.py:161: UserWarning: pylab import has clobbered these variables: ['colors', 'log']
`\%matplotlib` prevents importing * from pylab and numpy
  "\textbackslash{}n`\%matplotlib` prevents importing * from pylab and numpy"

@@

    \subsubsection{Initiating matrices}\label{initiating-matrices}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}2}]:} \PY{n}{chr1} \PY{o}{=} \PY{l+m+mi}{1}
        \PY{n}{chr2} \PY{o}{=} \PY{n}{chr1}
        \PY{k}{print} \PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{chromosome 1: }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{, chromosome 2: }\PY{l+s+si}{\PYZpc{}s}\PY{l+s+s2}{\PYZdq{}}\PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr2}\PY{p}{)}
        \PY{c+c1}{\PYZsh{}print observed\PYZus{}mit\PYZus{}original.shape}
        \PY{n}{mit\PYZus{}original} \PY{o}{=} \PY{n}{readYamlIntensities}\PYZbs{}
        \PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{../data/GM12878\PYZus{}primary/500kb\PYZus{}resolution\PYZus{}intrachromosomal/chr}\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s1}{/MAPQG0/chr}\PY{l+s+si}{\PYZpc{}d}\PY{l+s+s1}{\PYZus{}500kb.RAWobserved}\PY{l+s+s1}{\PYZsq{}}\PYZbs{}
         \PY{o}{\PYZpc{}}\PY{p}{(}\PY{n}{chr1}\PY{p}{,} \PY{n}{chr1}\PY{p}{)}\PY{p}{,} \PY{l+m+mi}{500000}\PY{p}{)}

@@

        \PY{c+c1}{\PYZsh{}There are some blank rows and columns in the matrix. let\PYZsq{}s remove them.}
        \PY{n}{blankRows4}\PY{p}{,} \PY{n}{blankCols4} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{mit\PYZus{}original}\PY{p}{)}
        \PY{n}{blankRows0}\PY{p}{,} \PY{n}{blankCols0} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
        \PY{n}{blankRows1}\PY{p}{,} \PY{n}{blankCols1} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}
        \PY{n}{blankRows2}\PY{p}{,} \PY{n}{blankCols2} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{rl}\PY{p}{)}
        \PY{n}{blankRows3}\PY{p}{,} \PY{n}{blankCols3} \PY{o}{=} \PY{n}{getBlankRowsAndColumns}\PY{p}{(}\PY{n}{call4}\PY{p}{)}
        \PY{n}{blankRows} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
        \PY{n}{blankCols} \PY{o}{=} \PY{n}{Set}\PY{p}{(}\PY{p}{[}\PY{p}{]}\PY{p}{)}
        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows0}\PY{p}{)}
        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows1}\PY{p}{)}
        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows2}\PY{p}{)}
        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows3}\PY{p}{)}
        \PY{n}{blankRows}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankRows4}\PY{p}{)}
        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols0}\PY{p}{)}
        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols1}\PY{p}{)}
        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols2}\PY{p}{)}
        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols3}\PY{p}{)}
        \PY{n}{blankCols}\PY{o}{.}\PY{n}{update}\PY{p}{(}\PY{n}{blankCols4}\PY{p}{)}
        \PY{n}{mit\PYZus{}original} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{mit\PYZus{}original}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
        \PY{n}{mit} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{mit}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
        \PY{n+nb}{all} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n+nb}{all}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
        \PY{n}{rl} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{rl}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
        \PY{n}{call4} \PY{o}{=} \PY{n}{removeRowsAndColumns}\PY{p}{(}\PY{n}{call4}\PY{p}{,} \PY{n}{blankRows}\PY{p}{,} \PY{n}{blankCols}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
chromosome 1: 1, chromosome 2: 1
file directory: ../data/extracted\_all\_contact\_MIT/chr\_01\_01\_500kb.mat
file directory: ../data/extracted\_all\_contact\_call4/chr\_01\_01\_500kb.mat
file directory: ../data/extracted\_all\_contact\_RL/chr\_01\_01\_500kb.mat
file directory: ../data/extracted\_all\_contact\_ALL/chr\_01\_01\_500kb.mat
size of old matrix: (499, 499)
size of new matrix: (456, 456)
size of old matrix: (495, 495)
size of new matrix: (452, 452)
size of old matrix: (495, 495)
size of new matrix: (452, 452)
size of old matrix: (495, 495)
size of new matrix: (452, 452)
size of old matrix: (495, 495)
size of new matrix: (452, 452)

@@

    \subsubsection{Comparing MIT with the Rao et al high-resolution
data:}\label{comparing-mit-with-the-rao-et-al-high-resolution-data}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}12}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{20}\PY{p}{)}
         \PY{n}{k} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{)}
         \PY{n}{method} \PY{o}{=} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{max}\PY{l+s+s1}{\PYZsq{}}
         \PY{n}{t} \PY{o}{=} \PY{l+m+mi}{0}
         \PY{n}{params} \PY{o}{=} \PY{n+nb+bp}{None}
         \PY{n}{symmetric}\PY{o}{=}\PY{n+nb+bp}{True}
         \PY{n}{call4\PYZus{}os} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{call4}\PY{o}{+}\PY{l+m+mi}{1}\PY{o}{+}\PY{l+m+mf}{1e\PYZhy{}5}\PY{p}{)}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{n}{k}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{n}{method}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{n}{t}\PY{p}{,} \PY{n}{params}\PY{o}{=}\PY{n}{params}\PY{p}{,} \PY{n}{symmetric}\PY{o}{=}\PY{n}{symmetric}\PY{p}{)}
         \PY{n}{rl\PYZus{}os} \PY{o}{=} \PY{n}{local\PYZus{}threshold}\PY{p}{(}\PY{p}{(}\PY{p}{(}\PY{n}{rl}\PY{o}{+}\PY{l+m+mi}{1}\PY{o}{+}\PY{l+m+mf}{1e\PYZhy{}5}\PY{p}{)}\PY{p}{)}\PY{p}{,} \PY{n}{k} \PY{o}{=} \PY{n}{k}\PY{p}{,} \PY{n}{method}\PY{o}{=}\PY{n}{method}\PY{p}{,} \PY{n}{t} \PY{o}{=} \PY{n}{t}\PY{p}{,} \PY{n}{params}\PY{o}{=}\PY{n}{params}\PY{p}{,} \PY{n}{symmetric}\PY{o}{=}\PY{n}{symmetric}\PY{p}{)}
         \PY{n}{n1}\PY{p}{,} \PY{n}{m1} \PY{o}{=} \PY{n}{call4\PYZus{}os}\PY{o}{.}\PY{n}{shape}
         \PY{n}{n2}\PY{p}{,} \PY{n}{m2} \PY{o}{=} \PY{n}{rl\PYZus{}os}\PY{o}{.}\PY{n}{shape}
         \PY{n}{n} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{n1}\PY{p}{,} \PY{n}{n2}\PY{p}{]}\PY{p}{)}
         \PY{n}{m} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{min}\PY{p}{(}\PY{p}{[}\PY{n}{m1}\PY{p}{,} \PY{n}{m2}\PY{p}{]}\PY{p}{)}
         \PY{n}{call4\PYZus{}os} \PY{o}{=} \PY{n}{call4\PYZus{}os}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
         \PY{n}{call4} \PY{o}{=} \PY{n}{call4}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
         \PY{n}{rl\PYZus{}os} \PY{o}{=} \PY{n}{rl\PYZus{}os}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
         \PY{n}{rl} \PY{o}{=} \PY{n}{rl}\PY{p}{[}\PY{p}{:}\PY{n}{n}\PY{p}{,} \PY{p}{:}\PY{n}{m}\PY{p}{]}
         \PY{n}{a} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{n}{call4\PYZus{}os} \PY{o}{*} \PY{n}{call4}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{l+m+mi}{1}
         \PY{n}{b} \PY{o}{=} \PY{p}{(}\PY{p}{(}\PY{n}{rl\PYZus{}os} \PY{o}{*} \PY{n}{rl}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{)} \PY{o}{*} \PY{l+m+mi}{1}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
(2, 2, 2, 2)
(2, 2, 2, 2)

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}17}]:} \PY{n}{images} \PY{o}{=} \PY{p}{[} \PY{n}{rl}\PY{p}{,} \PY{n}{a}\PY{p}{,} \PY{p}{(}\PY{n}{a}\PY{o}{\PYZhy{}}\PY{n}{b}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{l+m+mi}{0}\PY{p}{,} \PY{n}{call4}\PY{p}{,}  \PY{n}{b}\PY{p}{,} \PY{n}{a} \PY{o}{*} \PY{n}{b} \PY{p}{]}
         \PY{n}{titles} \PY{o}{=} \PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Thresholded RL}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Difference}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Thresholded CALL4}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Simmilarity}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}
         \PY{n}{showImages}\PY{p}{(}\PY{n}{images}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{titles}\PY{o}{=}\PY{n}{titles}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Number of columnts: 3

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_6_1.png}
    \end{center}
    { \hspace*{\fill} \\}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}22}]:} \PY{n}{pylab}\PY{o}{.}\PY{n}{rcParams}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{figure.figsize}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{p}{(}\PY{l+m+mi}{15}\PY{p}{,} \PY{l+m+mi}{9}\PY{p}{)}

         \PY{n}{n0}\PY{p}{,} \PY{n}{m0} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{mit}\PY{p}{)}
         \PY{n}{n1}\PY{p}{,} \PY{n}{m1} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{call4}\PY{p}{)}
         \PY{n}{n2}\PY{p}{,} \PY{n}{m2} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n}{rl}\PY{p}{)}
         \PY{n}{n3}\PY{p}{,} \PY{n}{m3} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{shape}\PY{p}{(}\PY{n+nb}{all}\PY{p}{)}

@@

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_7_1.png}
    \end{center}
    { \hspace*{\fill} \\}
